---
title: "Lecture 1 Experiment"
author: "Marcelo da Mata Oliveira"
output: pdf_document
---

\section*{Introduction}
In ophthalmology there are many tests that can perform in a non invasive way. In order to do that automatically we will use a smartphone to perform a psychophysical tests.

We can control the intensity of a point in the screen of smartphone by absolute values, but we want this values in a standard measurement unit, wich is commonly used by professionals of this field.

This report will describe how we made our experiment and show some results got.

\section*{Method}
We used a device called luximetry to get measurements of a point's intensities in the screen. In order to block the light from outside, we built a small paperboard box and we painted it inside with black color to minimize possible effects light reflectance.

The point area painted in the screen was measured in 3 different sizes, with diameters of 300, 200 and 100 millimeters.

\section*{Results}

```{r}
library(dplyr)
library(ggplot2)
library(reshape)
df = read.csv("C:/workspaces/ufrgs_4/SMPE/lectures/lecture 2/set1.csv", header=T)

measurements <- read.csv2("C:/workspaces/ufrgs_4/SMPE/lectures/homework_lecture_1/Measurements.csv", 
                          header = TRUE, sep = ";", quote="\"", dec=".",fill = TRUE)
summary(measurements)

```

```{r, echo=FALSE}
plot(df)

plot(measurements$X100mm, xlab="absolute", ylab="lux")
title("100 mm", font.main=2, adj=1)
plot(measurements$X200mm, xlab="absolute", ylab="lux")
title("200 mm", font.main=2, adj=1)
plot(measurements$X300mm, xlab="absolute", ylab="lux")
title("300 mm", font.main=2, adj=1)
```


Note that, the luximeter can't measure the first values in all sizes measured. So it's necessary fit these first values. Take a look again to last 3 plots of the measurements. Note that the curve has a polynomial behavior. Firstly we are going to fit them with a 2 degree polynomial.
